### 2016-01-23 p02-ch01-2014/paper.tex
Fix uncited references from imported papers

\section{Introduction}
\label{sec:introduction}
Java is beyond doubt one of the mainstream object oriented programming languages 
that supports a \emph{programming to interfaces} discipline \cite{oop:patterns,oop:survey}.
Through the years, Java has evolved from a mere programming language to a huge platform to drive and envision standards for mission-critical business applications.
Moreover, the Java language itself has evolved in these years to support its community with new language features and standards.
One of the noticeable domains of focus in the past decade has been distribution and concurrency in research and application.
This has led to valuable research results and numerous libraries and frameworks with an attempt to provide distribution and concurrency at the level of Java language.
However, it is widely recognized that the thread-based model of concurrency in Java that is a well-known approach is not appropriate for realizing distributed systems because of its inherent synchronous communication model.
On the other hand, the event-driven actor model of concurrency introduced by Hewitt \cite{Hewitt69} is 
a powerful concept for modeling distributed and concurrent
systems \cite{Agha90,Agha97}. 
Different extensions of actors are proposed in several domains and are claimed to be the most suitable model of computation for many  applications \cite{Hewitt07-commitment}. 
Examples of these domains include designing embedded systems \cite{LeeACtorEmbedded03,LeeLN09}, 
wireless sensor networks \cite{CheongSensor05}, multi-core programming \cite{KarmaniSA09} 
and delivering cloud services through SaaS or PaaS \cite{Chang:DAIS07}.
This model of concurrent computation forms the basis of the
programming languages Erlang \cite{Armstrong10Erlang} and Scala
\cite{haller09tcs} that have recently gained in popularity, in part
due to their support for scalable concurrency.  Moreover, based on the
Java language itself, there are numerous libraries  that
provide  an implementation of an actor-based programming model.

@@

We discuss next the distribution of actors in this architecture.
In the architecture presented  in Figure~\ref{fig:actors:arch}, each layer can be \emph{distributed} independently of another layer in a transparent way.
Not only the routing layer can provide distribution, the queue layer of the architecture may also be remote to take advantage of cluster storage for actor messages. 
A remote routing layer can provide access to actors transparently through standard naming or addresses.
% The implementation of remote actors is left as an the extension or plugin that is injected into the system.
% For instance, an extension may choose to provide remote actor access through HTTP layer; however, another may opt for a network layer implementation.
We exploit the main properties of actor model~\cite{Agha97,Agha90} to distribute actors based on our implementation.
From a distributed perspective, the following are the main requirements for  distributing actors:
\begin{description}
\item[Reference Location Transparency] 
Actors communicate to one another using references. 
In an actor model, there is no in-memory object reference; however, every actor reference denotes a location by means of which the actor is accessible.
The reference location may be local to the calling actor or remote.
The reference location is \emph{physically} transparent for the calling actor.
\item[Communication Transparency]
A message $m$ from actor $A$ to actor $B$ may possibly lead to transferring $m$ over a network such that $B$ can process the message.
Thus, an actor model that supports distribution must provide a layer of remote communication among its actors that is transparent, i.e., 
when actor $A$ sends message $m$, the message is transparently transferred over the network to reach actor $B$.
For instance, actors existing in an HTTP container that transparently allows such communication.
Further, the API implementation is required to provide a mechanism for serialization of messages.
By default, every object in JVM cannot be assumed to be an instance of \jtt{java.io.Serializable}.
However, the API may enforce  that any remote actor should have the required actor classes in its JVM during runtime which
allows the use of the JVM's general object serialization
\footnote{Java Object Serialization Specification: \surl{http://docs.oracle.com/javase/8/docs/platform/serialization/spec/serialTOC.html}}
to send messages to remote actors and receive their responses.
Additionally, we model asynchronous messages with lambda expressions for which Java~8 supports serialization by specification
\footnote{Serialized Lambdas: \surl{http://docs.oracle.com/javase/8/docs/api/java/lang/invoke/SerializedLambda.html}}.
\item[Actor Provisioning]
During a life time of an actor, it may need to create new actors.
Creating actors in a local memory setting is straightforward. 
However, the local setting \emph{does} have a capacity of number of actors it can hold.
When an actor creates a new one, the new actor may actually be initialized in a remote resource.
When the resource is not available, it should be first provisioned.
However, this resource provisioning should be transparent to the actor and only the eventual result (the newly created actor) is visible.
\end{description}

@@

The underlying modeling language has an executable semantics
and supports a variety of formal analysis techniques, including
deadlock and schedulability analysis \cite{GiachinoGLLW13,JaghooriBCS09}.
Further it supports a formal 
behavioral specification of interfaces \cite{HahnleHJLSSW11}, to be used as contracts.

>>>>

\section{Introduction}
\label{sec:introduction}
Java is beyond doubt one of the mainstream object oriented programming languages 
that supports a \emph{programming to interfaces} discipline \cite{oop:patterns,oop:survey}.
Through the years, Java has evolved from a mere programming language to a huge platform to drive and envision standards for mission-critical business applications.
Moreover, the Java language itself has evolved in these years to support its community with new language features and standards.
One of the noticeable domains of focus in the past decade has been distribution and concurrency in research and application.
This has led to valuable research results and numerous libraries and frameworks with an attempt to provide distribution and concurrency at the level of Java language.
However, it is widely recognized that the thread-based model of concurrency in Java that is a well-known approach is not appropriate for realizing distributed systems because of its inherent synchronous communication model.
On the other hand, the event-driven actor model of concurrency introduced by Hewitt \cite{Hewitt69} is 
a powerful concept for modeling distributed and concurrent
systems \cite{Agha90,agha97}. 
Different extensions of actors are proposed in several domains and are claimed to be the most suitable model of computation for many  applications \cite{Hewitt07-commitment}. 
Examples of these domains include designing embedded systems \cite{LeeACtorEmbedded03,LeeLN09}, 
wireless sensor networks \cite{CheongSensor05}, multi-core programming \cite{KarmaniSA09} 
and delivering cloud services through SaaS or PaaS \cite{Chang:DAIS07}.
This model of concurrent computation forms the basis of the
programming languages Erlang \cite{Armstrong10Erlang} and Scala
\cite{haller09tcs} that have recently gained in popularity, in part
due to their support for scalable concurrency.  Moreover, based on the
Java language itself, there are numerous libraries  that
provide  an implementation of an actor-based programming model.

@@

We discuss next the distribution of actors in this architecture.
In the architecture presented  in Figure~\ref{fig:actors:arch}, each layer can be \emph{distributed} independently of another layer in a transparent way.
Not only the routing layer can provide distribution, the queue layer of the architecture may also be remote to take advantage of cluster storage for actor messages. 
A remote routing layer can provide access to actors transparently through standard naming or addresses.
% The implementation of remote actors is left as an the extension or plugin that is injected into the system.
% For instance, an extension may choose to provide remote actor access through HTTP layer; however, another may opt for a network layer implementation.
We exploit the main properties of actor model~\cite{agha97,Agha90} to distribute actors based on our implementation.
From a distributed perspective, the following are the main requirements for  distributing actors:
\begin{description}
\item[Reference Location Transparency] 
Actors communicate to one another using references. 
In an actor model, there is no in-memory object reference; however, every actor reference denotes a location by means of which the actor is accessible.
The reference location may be local to the calling actor or remote.
The reference location is \emph{physically} transparent for the calling actor.
\item[Communication Transparency]
A message $m$ from actor $A$ to actor $B$ may possibly lead to transferring $m$ over a network such that $B$ can process the message.
Thus, an actor model that supports distribution must provide a layer of remote communication among its actors that is transparent, i.e., 
when actor $A$ sends message $m$, the message is transparently transferred over the network to reach actor $B$.
For instance, actors existing in an HTTP container that transparently allows such communication.
Further, the API implementation is required to provide a mechanism for serialization of messages.
By default, every object in JVM cannot be assumed to be an instance of \jtt{java.io.Serializable}.
However, the API may enforce  that any remote actor should have the required actor classes in its JVM during runtime which
allows the use of the JVM's general object serialization
\footnote{Java Object Serialization Specification: \surl{http://docs.oracle.com/javase/8/docs/platform/serialization/spec/serialTOC.html}}
to send messages to remote actors and receive their responses.
Additionally, we model asynchronous messages with lambda expressions for which Java~8 supports serialization by specification
\footnote{Serialized Lambdas: \surl{http://docs.oracle.com/javase/8/docs/api/java/lang/invoke/SerializedLambda.html}}.
\item[Actor Provisioning]
During a life time of an actor, it may need to create new actors.
Creating actors in a local memory setting is straightforward. 
However, the local setting \emph{does} have a capacity of number of actors it can hold.
When an actor creates a new one, the new actor may actually be initialized in a remote resource.
When the resource is not available, it should be first provisioned.
However, this resource provisioning should be transparent to the actor and only the eventual result (the newly created actor) is visible.
\end{description}

@@

The underlying modeling language has an executable semantics
and supports a variety of formal analysis techniques, including
deadlock and schedulability analysis \cite{GiachinoGLLW13,JaghooriBCS09}.
Further it supports a formal 
behavioral specification of interfaces \cite{hahnlehjlssw11}, to be used as contracts.
